A pandemic-scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-09-28 latex/main.tex

We also found highly recurrent deletions using the ARG.
The top 20 deletions in the number of occurrences in the ARG
are shown in Table~\ref{tab:rec_dels}.
About half of these deletions are one-base and
occur in the non-coding regions in the 3' end of the genome
between the accessory genes.
Four one-base deletions occur
in the accessory genes ORF7a, ORF8, and ORF10.
The two deletions in S1-NTD are known recurrent deletions
associated with antibody escape \cite{McCarthy2021}.

>>>>

We found highly recurrent deletions using the ARG,
for example, the top 20 deletions in terms of
the number of occurrences in the ARG
shown in Table~\ref{tab:rec_dels}.
About half of these deletions are one-base and
occur in the 5' or 3' UTR of the SARS-CoV-2 genome,
which are enriched for poor-quality sequencing data.
Genuine recurrent deletions are also captured in the ARG,
for example, two known recurrent deletions in S1-NTD
associated with antibody escape \cite{McCarthy2021}.
In-depth analysis of the deletions in the ARG
is beyond the scope of this study,
but we believe that the ARG will greatly
facilitate future evolutionary studies of
deletions in SARS-CoV-2.
